---
title: 'meet(R) in Tricity #3'
output:
  word_document: default
  html_notebook: default
  pdf_document: default
  html_document: default
---

```{r echo=FALSE}
library(readOffice)
library(DataEntry)
library(outreg)
library(huxtable)
library(RInno)
library(doctr)
library(tidyverse)
library(RODBC)
library(RJDBC)
library(RMySQL)


```

# readOffice

```{r}

#read_docx

word <- read_docx(docx=system.file('extdata','example.docx',package='readOffice'))

word


word_2 <- read_docx(docx='readOffice_example.docx')

word_2


#read_pptx

powerPoint <- read_pptx('read_pptx_ex.pptx')

powerPoint


```

# DataEntry -  Make it Easier to Enter Questionnaire Data

```{r}

DataEntry()


```

# outreg - Regression Table for Publication

lm, glm, survreg (Regression Survival Model), ivreg (instrumental variable regression)
```{r}

outreg_stat_list()

fit <- lm(mpg ~ cyl, data = mtcars)

outreg(fit)

fitlist <- list(lm(mpg ~ cyl, data = mtcars),
                lm(mpg ~ cyl + wt + hp, data = mtcars),
                lm(mpg ~ cyl + wt + hp + drat, data = mtcars))
outreg(fitlist)


```

# huxtable - Simply Create LaTeX and HTML Tables

```{r}

dfr <- data.frame(a = 1:5, b = letters[1:5], stringsAsFactors = FALSE)
dfr
ht <-  as_huxtable(dfr)

ht

to_html(ht)

ht_b <- set_all_borders(ht, 1:5, 1:2, 1)

ht_b

text_color(ht_b) <- 'navy'

ht_b

theme_article(ht)




```

#  RInno - A Local Deployment Framework for Shiny Apps

```{r}

create_app(app_name='my_appek', app_dir = getwd(), dir_out = "RInno_installer", pkgs = c("jsonlite", "shiny", "magrittr"), include_R = F, R_version = paste0(R.version$major, ".", R.version$minor))



```

# doctr - Easily Check Data Consistency and Quality

> A tool that helps you check the consistency and the
quality of data. Like a real doctor, it has functions for examining,
diagnosing and assessing the progress of its ``patients''.



```{r}


is_character(mtcars$mpg)



mtcars %>% compare(mtcars) %>% issues(verbose=TRUE)

mtcars_1 <- mtcars[,1:5]

mtcars %>% compare(mtcars_1) %>% issues(verbose=TRUE)



```
# iMessager 

tylko macOS ...

```{r}

#send.imessage(recipient, message)



#send.imessage("nr telefonu/adre email","Hello World!")
```


# SQL


channel <- odbcConnect("DATABASE", uid="USERNAME", pwd="PASSWORD", believeNRows=FALSE)

# Check that connection is working (Optional)
odbcGetInfo(channel)

# Find out what tables are available (Optional)
Tables <- sqlTables(channel, schema="SCHEMA")

# Query the database and put the results into the data frame "dataframe"
 dataframe <- sqlQuery(channel, "
 SELECT * FROM SCHEMA.DATATABLE")
 
 





